---
title: "other diseases data collection"
output: html_document
date: "2023-07-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library, message=FALSE, warning=FALSE}
library(httr)
library(jsonlite)
library(tidyverse)
library(flextable)
```

```{r}
diseaseId <- "2,3,4,5,6,8,10,11,12,13,14,15,16,17,18,20,22,23,24,26,27,28,29,31,32,35,36,37,38,39,40,41,43,44,46,47,48,49,50,51,52,53,54,55,57,58,59,60,61,63,64,65,66,67,68,69,70,72,73,74,75,76,77,81,83,84,86,87,88,89,90,92,94,95,97,99,100,101,103,107,108,109,110,112,113,114,115,117,119,122,123,124,125,128,131,132,134,135,136,141,146,149,150,153,156,160,161,162,163,172,175,183,194,195,196,197,198,199,200,201,202,203,204,205,206,207,208,209,210,211,212,213,215,216,224,225,231,232,239,248,260,261,264,269,270,272,273,275"

startDate <- "&startDate=2023-08-13"
endDate <- "&endDate=2023-08-19"
```

# Indonesia
## News Sources
```{r}
inaUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1643084?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(inaUrl, add_headers("Ocp-Apim-Subscription-Key" = "371e207132a2497f8e981a8d3264788b", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
inaNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  inaNews <- rbind(inaNews, vec)
}
flextable(inaNews)
```

## Aggregated
```{r}
inaUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1643084?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(inaUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
#inaData <- data.frame(t(sapply(res$data,c)))
inaData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(inaData)
```


# Brunei Darussalam
## News
```{r}
brnUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1820814?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(brnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
brnNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  brnNews <- rbind(brnNews, vec)
}
flextable(brnNews)
```

## Aggregate
```{r}
brnUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1820814?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(brnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
brnData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(brnData)
```

# Cambodia
## News
```{r}
khmUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1831722?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(khmUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
khmNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  khmNews <- rbind(khmNews, vec)
}
flextable(khmNews)
```

## Aggregate
```{r}
khmUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1831722?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(khmUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
khmData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(khmData)
```

# Lao PDR
## News
```{r}
laoUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1655842?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(laoUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
laoNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  laoNews <- rbind(laoNews, vec)
}
flextable(laoNews)
```

## Aggregate
```{r}
laoUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1655842?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(laoUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
laoData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(laoData)
```

# Malaysia
## News
```{r}
mlyUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1733045?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(mlyUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
mlyNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  mlyNews <- rbind(mlyNews, vec)
}
flextable(mlyNews)
```

## Aggregate
```{r}
mlyUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1733045?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(mlyUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
mlyData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(mlyData)
```

# Myanmar
## News
```{r}
myrUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1327865?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(myrUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
myrNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  myrNews <- rbind(myrNews, vec)
}
flextable(myrNews)
```
## Aggregate
```{r}
myrUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1327865?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(myrUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
myrData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(myrData)
```



# Philippines
## News
```{r}
phlUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1694008?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(phlUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
phlNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  phlNews <- rbind(phlNews, vec)
}
flextable(phlNews)
```

## Aggregate
```{r}
phlUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1694008?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(phlUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
phlData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(phlData)
```

# Singapore
## News
```{r}
sgpUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1880251?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(sgpUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
sgpNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  sgpNews <- rbind(sgpNews, vec)
}
flextable(sgpNews)
```

## aggregate
```{r}
sgpUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1880251?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(sgpUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
sgpData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(sgpData)
```

# Thailand
```{r}
thaUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1605651?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(thaUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
thaNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  thaNews <- rbind(thaNews, vec)
}
flextable(thaNews)
```

## Aggregate
```{r}
thaUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1605651?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(thaUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
thaData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(thaData)
```

# Vietnam
## News
```{r}
vnmUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1562822?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(vnmUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
vnmNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  vnmNews <- rbind(vnmNews, vec)
}
flextable(vnmNews)
```

## Aggregate
```{r}
vnmUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1562822?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(vnmUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
vnmData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(vnmData)
```

# China
## News
```{r}
chnUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1814991?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(chnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
chnNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  chnNews <- rbind(chnNews, vec)
}
flextable(chnNews)
```

## Aggregate
```{r}
chnUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1814991?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(chnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
chnData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(chnData)
```

# South Korea
## News
```{r}
korUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1835841?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(korUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
korNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  korNews <- rbind(korNews, vec)
}
flextable(korNews)
```

## Aggregate
```{r}
korUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1835841?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(korUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
korData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(korData)
```

# Japan
## News
```{r}
jpnUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1861060?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(jpnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
jpnNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  jpnNews <- rbind(jpnNews, vec)
}
flextable(jpnNews)
```

## Aggregate
```{r}
jpnUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1861060?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(jpnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
jpnData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(jpnData)
```

# Taiwan
## News
```{r}
twnUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1668284?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(twnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
twnNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  twnNews <- rbind(twnNews, vec)
}
flextable(twnNews)
```

## Aggregate
```{r}
twnUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1668284?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(twnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
twnData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(twnData)
```

# Hong kong
## News
```{r}
hkgUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1819730?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(hkgUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
hkgNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  hkgNews <- rbind(hkgNews, vec)
}
flextable(hkgNews)
```

## Aggregate
```{r}
hkgUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1819730?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(hkgUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
hkgData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(hkgData)
```

# Macau
## News
```{r}
macUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1821275?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(macUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
macNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  macNews <- rbind(macNews, vec)
}
flextable(macNews)
```

## Aggregate
```{r}
macUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1821275?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(macUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
macData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(macData)
```

# Timor Leste
## News
```{r}
tlsUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1966436?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=false&includeSources=true&api-version=v1")
res <- GET(tlsUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
tlsNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  tlsNews <- rbind(tlsNews, vec)
}
flextable(tlsNews)
```

## Aggregate
```{r}
tlsUrl <- paste0("https://developer.bluedot.global/casecounts/locations/1966436?diseaseIds=", diseaseId, startDate, endDate, "&isAggregated=true&includeSources=false&api-version=v1")
res <- GET(tlsUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
tlsData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(tlsData)
```

# Dengue Cases
```{r}
dengueUrl <- paste0("https://developer.bluedot.global/casecounts/diseases/55?locationIds=1820814,%201831722,%201643084,%201655842,%201733045,%201327865,%201694008,%201880251,%201605651,%201562822,%201861060,%201835841,%201814991", "&startDate=2023-01-01", endDate, "&isAggregated=true&api-version=v1")
res <- GET(dengueUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
dengueData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(dengueData)
```

# Malaria Cases
```{r}
malariaUrl <- paste0("https://developer.bluedot.global/casecounts/diseases/141?locationIds=1820814,%201831722,%201643084,%201655842,%201733045,%201327865,%201694008,%201880251,%201605651,%201562822,%201861060,%201835841,%201814991", "&startDate=2023-01-01", endDate, "&isAggregated=true&api-version=v1")
res <- GET(malariaUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
malariaData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(malariaData)
```

# Measles Cases
```{r}
measlesUrl <- paste0("https://developer.bluedot.global/casecounts/diseases/10?locationIds=1820814,%201831722,%201643084,%201655842,%201733045,%201327865,%201694008,%201880251,%201605651,%201562822,%201861060,%201835841,%201814991", "&startdate=2023-01-01", endDate, "&isAggregated=true&api-version=v1")
res <- GET(measlesUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
measlesData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(measlesData)
```

# Rabies Cases
```{r}
rabiesUrl <- paste0("https://developer.bluedot.global/casecounts/diseases/43?locationIds=1820814,%201831722,%201643084,%201655842,%201733045,%201327865,%201694008,%201880251,%201605651,%201562822,%201861060,%201835841,%201814991", "&startDate=2023-01-01", endDate, "&isAggregated=true&api-version=v1")
res <- GET(rabiesUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
rabiesData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(rabiesData)
```