---
title: "other diseases data collection"
output: html_document
date: "2023-07-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library, message=FALSE, warning=FALSE, include=FALSE}
library(httr)
library(jsonlite)
library(tidyverse)
library(gt)
library(kableExtra)
library(zoo)
```

```{r setting date and default diseases}
startDate <- "2024-07-21"
endDate <- "2024-07-27"
disease <- "15,141,83,164,84,166,55,53,88,38,63,13,4,205,10,43,26,153,156,162,6,110,113,136,212,215,216,224,264,200,41,40,39,37,64,239,47"
ams <- "1880251,1605651,1694008,1820814,1733045,1643084,1831722,1327865,1655842,1562822"
country <- "2077456,1814991,1819730,102358,1835841,1668284,290557,2635167,1861060,1821275,289688,337996,1269750,2750405,2186224,286963,1168579,2017370,1227603,1966436,298795,1210997,2921044,130758,99237,248816,1522867,1282028,934292,1282988,6252001,1512440,290291,6251999,4043988,285570,1559582,2088628,1252634,2623032,2205218,660013,3017382,390903,3175395,798544,953987,2510769,2661886,2658434,2782113,2802361,357994,294640,192950,2029969,3144096,935317,1218197,690791"
```

# Disease Event from Bluedot Human Disease and Case API among AMS at national level
```{r}
url <- paste0("https://developer.bluedot.global/casecounts/?diseaseIds=", disease, "&subLocationTypes=6&startDate=", startDate, "&endDate=", endDate, "&isAggregated=FALSE&includeSources=TRUE&includeCsv=FALSE&api-version=v1")
res <- GET(url, add_headers("Ocp-Apim-Subscription-Key" = "52bd528ca9cd407394791ca418a7b409", "Cache-Control" = "no-cache")) |> content()
disease_event_national <- enframe(pluck(res, "data")) |> unnest_wider(value) |> filter(countryId %in% c(1880251,1605651,1694008,1820814,1733045,1643084,1831722,1327865,1655842,1562822)) |> 
  unnest(minSources) |> unnest_wider(minSources) |> select(!c(maxSources))
View(disease_event_national)
```

# Disease Event from Bluedot Human Disease and Case API among AMS at sub-national level
```{r}
url <- paste0("https://developer.bluedot.global/casecounts/?diseaseIds=", disease, "&subLocationTypes=4&startDate=", startDate, "&endDate=", endDate, "&isAggregated=FALSE&includeSources=TRUE&includeCsv=FALSE&api-version=v1")
res <- GET(url, add_headers("Ocp-Apim-Subscription-Key" = "52bd528ca9cd407394791ca418a7b409", "Cache-Control" = "no-cache")) |> content()
disease_event_subnational <- enframe(pluck(res, "data")) |> unnest_wider(value) |> filter(countryId %in% c(1880251,1605651,1694008,1820814,1733045,1643084,1831722,1327865,1655842,1562822)) |> 
  unnest(minSources) |> unnest_wider(minSources) |> select(!c(maxSources))
View(disease_event_subnational)
```

# Collect routine MMWR diseases from Bluedot
```{r}
mmwr <- "55,141,10,43,4,53"
url <- paste0("https://developer.bluedot.global/casecounts/?diseaseIds=", disease, "&locationIds=", ams, "&startDate=2024-01-01&endDate=", endDate, "&isAggregated=TRUE&includeSources=FALSE&includeCsv=FALSE&api-version=v1")
res <- GET(url, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
disease_aggr <- enframe(pluck(res, "data")) |> unnest_wider(value) |> 
  select(!c(name, reportedDate, locationId, locationName, latitude, longitude, locationType, minSources, maxSources))
View(disease_aggr)
```

# Indicator-based Surveillance Data from Bluedot
```{r cumulative}
ind_surv <- function(location, start_date) {
  url <- paste0("https://developer.bluedot.global/casecounts/indicator-based/?locationIds=", location, "&startDate=", start_date, "&api-version=v1")
  res <- GET(url, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
  data <- enframe(pluck(res, "data")) |> unnest_wider(value)
  return(data)
}
```

```{r}
data <- ind_surv(location = "1880251,1605651,1694008,1820814,1733045,1643084,1831722,1327865,1655842,1562822", start_date = "2024-04-01")
View(data)
```


```{r weekly}
sgpUrl <- "https://developer.bluedot.global/casecounts/indicator-based/?locationIds=1880251&startDate=2023-12-03&sourceOrgNames=Ministry%20of%20Health%20Singapore&api-version=v1"
res <- GET(sgpUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
sgpData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> 
  select(reportingPeriodStartEpiWeek, diseaseName, 
         totalReportedCases, totalConfirmedCases, totalDeaths) |> arrange(diseaseName)
flextable(sgpData)
#View(sgpData)
```

# Other countries (China, ROK, Japan, Taiwan, Hong Kong, Macau, Timor Leste)
```{r}
other <- "1814991,1835841,1861060,1668284,1819730,1821275,1966436"
url <- paste0("https://developer.bluedot.global/casecounts/?diseaseIds=", disease, "&locationIds=", other, "&startDate=", startDate, "&endDate=", endDate, "&isAggregated=true&includeSources=false&includeCsv=false&api-version=v1")
res <- GET(url, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
other_country_aggr <- enframe(pluck(res, "data")) |> unnest_wider(value) |> 
  select(!c(name, reportedDate, locationId, locationName, latitude, longitude, locationType, minSources, maxSources))
View(other_country_aggr)
```

```{r}
url <- paste0("https://developer.bluedot.global/casecounts/?diseaseIds=", disease, "&locationIds=", other, "&startDate=", startDate, "&endDate=", endDate, "&isAggregated=false&includeSources=false&includeCsv=false&api-version=v1")
res <- GET(url, add_headers("Ocp-Apim-Subscription-Key" = "52bd528ca9cd407394791ca418a7b409", "Cache-Control" = "no-cache")) |> content()
disease_event <- enframe(pluck(res, "data")) |> unnest_wider(value)
View(disease_event)
```

# Function to get data from Bluedot based on diseases among AMS
```{r}
bluedot_cases_aggr <- function(code, start_date, end_date){
  url <- paste0("https://developer.bluedot.global/casecounts/diseases/", code, "?locationIds=1880251,1605651,1694008,1820814,1733045,1643084,1831722,1327865,1655842,1562822&startDate=", start_date, "&endDate=", end_date, "&isAggregated=true&api-version=v1")
  res <- GET(url, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
  data <- enframe(pluck(res, "data")) |> unnest_wider(value) |> 
    select(diseaseName, locationName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
  return(data)
}

country_cases <- function(code, country, start_date, end_date){
  url <- paste0("https://developer.bluedot.global/casecounts/diseases/", code, "?locationIds=", country, "&startDate=", start_date, "&endDate=", end_date, "&isAggregated=false&includeSources=true&api-version=v1")
  res <- GET(url, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
  data <- enframe(pluck(res, "data")) |> unnest_wider(value) |> 
    select(diseaseName, locationName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths, sources) |> 
    unnest(sources) |> unnest_wider(sources)
  return(data)
}
```

```{r}
bluedot_cases_global <- function(code){
  url <- paste0("https://developer.bluedot.global/casecounts/diseases/", code, "?subLocationTypes=6", "&isAggregated=true&api-version=v1")
  res <- GET(url, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
  data <- enframe(pluck(res, "data")) |> unnest_wider(value) |> 
    select(diseaseName, locationName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
  return(data)
}
```

# Oropouche
```{r}
orov <- bluedot_cases_global(90) |> select(locationName, totalReportedCases, totalDeaths) |> pivot_longer(cols = c("totalReportedCases", "totalDeaths"), names_to = "report", values_to = "value")
```

```{r}
ggplot(orov, aes(x = locationName, y = value, fill = report)) + geom_col(position = "dodge") + geom_text(aes(label = value))
```


```{r}
data <- country_cases(code = 141, country = 1643084, start_date = "2024-01-01", end_date = "2024-05-11")
View(data)
```

# Legionellosis

```{r}
legionellosisData <- bluedot_cases(code = 99, start_date = "2023-01-01", end_date = "2023-12-31")
```

# Nipah

```{r}
nipahData <- bluedot_cases(code = 41, start_date = "2023-01-01", end_date = "2023-12-31")
```

# Ethiopia

## News

```{r}
url <- "https://developer.bluedot.global/casecounts/locations/337996?startDate=2023-01-01&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(url, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
news <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  news <- rbind(news, vec)
}
flextable(news)
```

## Aggregate

```{r}
url <- "https://developer.bluedot.global/casecounts/locations/337996?diseaseIds=&startDate=2023-01-01&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(url, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
data <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(data)
```

# Zika

```{r}
zikaUrl <- paste0("https://developer.bluedot.global/casecounts/diseases/88?locationIds=1820814,%201831722,%201643084,%201655842,%201733045,%201327865,%201694008,%201880251,%201605651,%201562822,%201861060,%201835841,%201814991&startDate=2023-09-01&isAggregated=true&api-version=v1")
res <- GET(zikaUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
zikaData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(zikaData)
```

# Chikungunya Cases

```{r}
chikungunyaUrl <- paste0("https://developer.bluedot.global/casecounts/diseases/53?locationIds=1820814,%201831722,%201643084,%201655842,%201733045,%201327865,%201694008,%201880251,%201605651,%201562822,%201861060,%201835841,%201814991&startDate=2023-01-01&endDate=", endDate, "&isAggregated=true&api-version=v1")
res <- GET(chikungunyaUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
chikungunyaData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(chikungunyaData)
```

# Pertussis

```{r}
zikaUrl <- paste0("https://developer.bluedot.global/casecounts/diseases/13?locationIds=1820814,%201831722,%201643084,%201655842,%201733045,%201327865,%201694008,%201880251,%201605651,%201562822,%201861060,%201835841,%201814991&startDate=2023-11-01&isAggregated=true&api-version=v1")
res <- GET(zikaUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
zikaData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(zikaData)
```

# TB

```{r}
zikaUrl <- paste0("https://developer.bluedot.global/casecounts/diseases/7?locationIds=1820814,%201831722,%201643084,%201655842,%201733045,%201327865,%201694008,%201880251,%201605651,%201562822,%201861060,%201835841,%201814991&startDate=2023-11-01&isAggregated=true&api-version=v1")
res <- GET(zikaUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
zikaData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
flextable(zikaData)
```

```{r}
url <- paste0("https://developer.bluedot.global/casecounts/diseases/", 88, "?locationIds=1966436&startDate=", startDate, "&endDate=", endDate, "&isAggregated=false&includeSources=false&api-version=v1")
res <- GET(url, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
data <- enframe(pluck(res, "data")) |> unnest_wider(value)
```

# Mpox
## From Event-based
```{r}
url <- paste0("https://developer.bluedot.global/casecounts/?diseaseIds=64&subLocationTypes=6&startDate=2024-01-01&isAggregated=FALSE&includeSources=TRUE&includeCsv=FALSE&api-version=v1")
res <- GET(url, add_headers("Ocp-Apim-Subscription-Key" = "52bd528ca9cd407394791ca418a7b409", "Cache-Control" = "no-cache")) |> content()
mpox <- enframe(pluck(res, "data")) |> unnest_wider(value) |> 
  unnest(minSources) |> unnest_wider(minSources) |> select(!c(maxSources)) |> 
  mutate(date = as.Date(publishedDate))
View(mpox)
```

```{r}
mpox_daily <- mpox |> group_by(countryName, date) |>
  summarise(num_case = sum(maxTotalReportedCases),
            num_death = sum(maxTotalDeaths))
View(mpox_daily)
```

```{r}
mpox_daily_wide <- mpox_daily |> 
  arrange(date) |> 
  pivot_longer(cols = c("num_case", "num_death"), names_to = "vars", values_to = "n") |> 
  pivot_wider(names_from = "date", values_from = "n", values_fill = 0)
```

```{r}
ggplot(mpox_daily, aes(x = date, y = num_case, colour = countryName)) + geom_line()
```

## From Indicator-based
```{r}
link <- "https://raw.githubusercontent.com/owid/monkeypox/main/owid-monkeypox-data.csv"
download.file(link, "mpox-owid.csv")
data <- read_csv("mpox-owid.csv")
world_data <- data |> 
  filter(iso_code %in% c("OWID_AFR", "OWID_ASI", "OWID_EUR", "OWID_NAM", "OWID_SAM", "OWID_OCE"), 
        date >= "2024-01-01") |> 
  mutate(new_cases_ma = rollmean(new_cases, k = 7, fill = NA))
```

```{r}
ggplot(world_data, aes(x = date, y = new_cases_smoothed, colour = location)) + geom_line()
```

