---
title: "other diseases data collection"
output: html_document
date: "2023-07-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library, message=FALSE, warning=FALSE}
library(httr)
library(jsonlite)
library(tidyverse)
library(DT)
```

# Indonesia
## News Sources
```{r}
inaUrl <- "https://developer.bluedot.global/casecounts/locations/1643084?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(inaUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
inaNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  inaNews <- rbind(inaNews, vec)
}
datatable(inaNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregated
```{r}
inaUrl <- "https://developer.bluedot.global/casecounts/locations/1643084?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(inaUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
#inaData <- data.frame(t(sapply(res$data,c)))
inaData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(inaData)
```


# Brunei Darussalam
## News
```{r}
brnUrl <- "https://developer.bluedot.global/casecounts/locations/1820814?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(brnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
brnNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  brnNews <- rbind(brnNews, vec)
}
datatable(brnNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregate
```{r}
brnUrl <- "https://developer.bluedot.global/casecounts/locations/1820814?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(brnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
brnData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(brnData)
```

# cambodia
## News
```{r}
khmUrl <- "https://developer.bluedot.global/casecounts/locations/1831722?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(khmUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
khmNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  khmNews <- rbind(khmNews, vec)
}
datatable(khmNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregate
```{r}
khmUrl <- "https://developer.bluedot.global/casecounts/locations/1831722?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(khmUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
khmData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(khmData)
```

# Lao PDR
## News

```{r}
laoUrl <- "https://developer.bluedot.global/casecounts/locations/1655842?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(laoUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
laoNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  laoNews <- rbind(laoNews, vec)
}
datatable(laoNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```
## Aggregate
```{r}
laoUrl <- "https://developer.bluedot.global/casecounts/locations/1655842?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(laoUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
laoData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(laoData)
```

# Malaysia
## News
```{r}
mlyUrl <- "https://developer.bluedot.global/casecounts/locations/1733045?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(mlyUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
mlyNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  mlyNews <- rbind(mlyNews, vec)
}
datatable(mlyNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregate
```{r}
mlyUrl <- "https://developer.bluedot.global/casecounts/locations/1733045?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(mlyUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
mlyData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(mlyData)
```

# Myanmar
## News
```{r}
myrUrl <- "https://developer.bluedot.global/casecounts/locations/1327865?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(myrUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
myrNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  myrNews <- rbind(myrNews, vec)
}
datatable(myrNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```
## Aggregate
```{r}
myrUrl <- "https://developer.bluedot.global/casecounts/locations/1327865?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(myrUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
myrData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(myrData)
```



# Philippines
## News
```{r}
phlUrl <- "https://developer.bluedot.global/casecounts/locations/1694008?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(phlUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
phlNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  phlNews <- rbind(phlNews, vec)
}
datatable(phlNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregate
```{r}
phlUrl <- "https://developer.bluedot.global/casecounts/locations/1694008?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(phlUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
phlData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(phlData)
```

# Singapore
## News
```{r}
sgpUrl <- "https://developer.bluedot.global/casecounts/locations/1880251?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(sgpUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
sgpNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  sgpNews <- rbind(sgpNews, vec)
}
datatable(sgpNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## aggregate
```{r}
sgpUrl <- "https://developer.bluedot.global/casecounts/locations/1880251?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(sgpUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
sgpData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(sgpData)
```

# Thailand
```{r}
thaUrl <- "https://developer.bluedot.global/casecounts/locations/1605651?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(thaUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
thaNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  thaNews <- rbind(thaNews, vec)
}
datatable(thaNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregate
```{r}
thaUrl <- "https://developer.bluedot.global/casecounts/locations/1605651?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(thaUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
thaData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(thaData)
```

# Vietnam
## News
```{r}
vnmUrl <- "https://developer.bluedot.global/casecounts/locations/1562822?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(vnmUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
vnmNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  vnmNews <- rbind(vnmNews, vec)
}
datatable(vnmNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregate
```{r}
vnmUrl <- "https://developer.bluedot.global/casecounts/locations/1562822?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-06-29&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(vnmUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
vnmData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(vnmData)
```

# China
## News
```{r}
chnUrl <- "https://developer.bluedot.global/casecounts/locations/1814991?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(chnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
chnNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  chnNews <- rbind(chnNews, vec)
}
datatable(chnNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregate
```{r}
chnUrl <- "https://developer.bluedot.global/casecounts/locations/1814991?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(chnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
chnData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(chnData)
```

# South Korea
## News
```{r}
korUrl <- "https://developer.bluedot.global/casecounts/locations/1835841?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(korUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
korNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  korNews <- rbind(korNews, vec)
}
datatable(korNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregate
```{r}
korUrl <- "https://developer.bluedot.global/casecounts/locations/1835841?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(korUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
korData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(korData)
```

# Japan
```{r}
jpnUrl <- "https://developer.bluedot.global/casecounts/locations/1861060?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(jpnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
jpnNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  jpnNews <- rbind(jpnNews, vec)
}
datatable(jpnNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregate
```{r}
jpnUrl <- "https://developer.bluedot.global/casecounts/locations/1861060?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(jpnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
jpnData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(jpnData)
```

# Taiwan
```{r}
twnUrl <- "https://developer.bluedot.global/casecounts/locations/1668248?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(twnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
twnNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  twnNews <- rbind(twnNews, vec)
}
datatable(twnNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregate
```{r}
twnUrl <- "https://developer.bluedot.global/casecounts/locations/1668248?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(twnUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
twnData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(twnData)
```

# Hong kong
```{r}
hkgUrl <- "https://developer.bluedot.global/casecounts/locations/1819730?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(hkgUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
hkgNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  hkgNews <- rbind(hkgNews, vec)
}
datatable(hkgNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregate
```{r}
hkgUrl <- "https://developer.bluedot.global/casecounts/locations/1819730?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(hkgUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
hkgData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(hkgData)
```

# Macau
```{r}
macUrl <- "https://developer.bluedot.global/casecounts/locations/1821275?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(macUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
macNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  macNews <- rbind(macNews, vec)
}
datatable(macNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregate
```{r}
macUrl <- "https://developer.bluedot.global/casecounts/locations/1821275?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(macUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
macData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(macData)
```

# Timor Leste
```{r}
tlsUrl <- "https://developer.bluedot.global/casecounts/locations/1966436?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=false&includeSources=true&api-version=v1"
res <- GET(tlsUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
length_df <- length(res$data)
tlsNews <- data.frame()
for(i in 1:length_df){
  disease_name <- pluck(res, "data", i, "diseaseName")
  vec <- enframe(pluck(res, "data", i, "sources")) |> unnest_wider(value)
  vec$name <- disease_name
  tlsNews <- rbind(tlsNews, vec)
}
datatable(tlsNews, options = list(
  searching = FALSE,
  autoWidth = TRUE,
  columnDefs = list(list(width = '100px', targets = "_all"))))
```

## Aggregate
```{r}
tlsUrl <- "https://developer.bluedot.global/casecounts/locations/1966436?diseaseIds=239,%20200,%2013,%2055,%20141,%2064,%2059,%2086,%2012,%2099,%20100,%2032,%206,%208,%2043,%2026,%2053,%2011,%20112,%20113,%20208&startDate=2023-07-04&isAggregated=true&includeSources=false&api-version=v1"
res <- GET(tlsUrl, add_headers("Ocp-Apim-Subscription-Key" = "5f645982e25d4a729d7292b890a8ed31", "Cache-Control" = "no-cache")) |> content()
tlsData <- enframe(pluck(res, "data")) |> unnest_wider(value) |> select(diseaseName, countryName, totalReportedCases, totalConfirmedCases, totalSuspectedCases, totalDeaths)
datatable(tlsData)
```

